Project Light

### 2015-09-09 paper/paper.tex
longer description of screenshot

\begin{figure}
	\centering
	\includegraphics[scale=.15]{images/screen_native.png}
	\caption{Screenshot of the native Android application used to encode the key and emit it as light flickering.}
	\label{fig:screenshot}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics[scale=.15]{images/screen_native.png}
	\caption{Screenshot of the native Android application used to encode the key and emit it as light flickering. With a toggle switch you can choose if you want the flashlight or the screen to flicker. The length of one bit can be adjusted using a slider. Any test entered in the text filed can be transmitted by tapping on ``start''. While transmitting, the user gets feedback about the current phase right above the buttons.}
	\label{fig:screenshot}
\end{figure}
